{\fontfamily{ptm}\selectfont Lorum ipsum}

### 2025-07-02 Notebook LaTEX/SAGD Under Interpolation/main-2025-06-30.tex
>w<, changes

\begin{document}

\title{{\fontfamily{ptm}\selectfont Lorum ipsum}}

@@

        \begin{definition}[Bregman Divergence]
            Let $f:\RR^n \rightarrow \overline \RR$ be a differentiable function. 
            Then, for all the Bregman divergence $D_f: \RR^n \times \dom\nabla f \rightarrow \RR$ is defined as: 
            \begin{align*}
                D_f(x, y) := f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
            \end{align*}
        \end{definition}
        \begin{remark}
            If, $f$ is $\mu \ge 0$ strongy convex and $L$ Lipschitz smooth then, its Bregman Divergence has for all $x, y \in \RR^n$: $\mu/2 \Vert x - y\Vert^2 \le D_f(x, y) \le L/2 \Vert x - y\Vert^2$. 
        \end{remark}

@@

        \begin{definition}[similar triangle representation of NAPG]\;\label{def:st-method}\\
            Let $(\alpha_k)_{k \ge 0}$ be an R-WAPG sequence. 
            Suppose that the base case $v_{-1}, x_{k - 1}\in \RR^n$ is given to initialize the algorithm. 
            Then the algorithm produces the sequence of iterates $(y_k, x_k, v_k)_{k \ge 0}$ and auxilary parameter sequence $L_k, \tau_k$ satisfying these inequalities: 
            \begin{align*}
                & \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}, 
                \\
                & y_k = (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1},
                \\
                & D_f(x_k, y_k) \le L_k/2\Vert x_k - y_k\Vert^2, 
                \\
                & x_k = T_{L_k}(y_k),
                \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
            \end{align*} 
        \end{definition}
        The following theorems are critical in analyzing the behavior of algorithm in Definition \ref{def:st-method}. 
        \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
            Let function $F$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, so it's $\mu \ge 0$ strongly convex. 
            For all $x\in \RR^n$, define $x^+ = T_L(x)$, then there exists a $B \ge 0$ such that $D_f(x^+, x) \le B/2 \Vert x^+ - x\Vert^2$. 
            Then, for all $z \in \RR^n$ it satisfies proximal gradient inequality at point $x$:  
            \begin{align*}
                0&\le F(z) - F(x^+) - \frac{B}{2}\Vert z - x^+\Vert^2  + \frac{B - \mu}{2}\Vert z - x\Vert^2
                \\
                &=  F(z) - F(x^+) - \langle B(x - x^+), z - x\rangle
                - \frac{\mu}{2}\Vert z - x\Vert^2
                - \frac{B}{2}\Vert x - x^+\Vert^2. 
            \end{align*}
            Since $f$ is assumed to be $L$ Lispchitz smooth, the above condition is true for all $x, y \in \RR^n$ for all $B \ge L$. 
        \end{theorem}
        \begin{remark}
            The theorem is the same as in Nesterov's book \cite[Theorem 2.2.13]{nesterov_lectures_2018}, but with the use of proximal gradient mapping and proximal gradient instead of project gradient hence making it equivalent to the theorem in Beck's book \cite[Theorem 10.16]{beck_first-order_2017}. 
            The only generalization here is parameter $B$ which made to accomodate algorithm that implements Definition \ref{def:st-method} with some line search routine. 
        \end{remark}
        \begin{theorem}[Jensen's inequality]\label{thm:jesen}
            Let $F: \RR^n \rightarrow \overline \RR$ be a $\mu \ge 0$ strongly convex function. 
            Then, it is equivalent to the following condition. 
            For all $x, y \in \RR^n$, $\lambda \in (0, 1)$ it satisfies the inequality 
            \begin{align*}
                (\forall \lambda \in [0, 1])\; 
                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert y - x\Vert^2. 
            \end{align*}
        \end{theorem}
        \begin{remark}
            If $x, y$ is out of $\dom F$, the inequality still work by convexity. 
        \end{remark}

@@

        The following theorem provide a complete proof for the convergence rate of algorithms implementing Definition \ref{def:st-method}, which is equivalent to NAG, or NAPG. 
        It made use of Definition \ref{def:rwapg-seq} which accomodates a relaxed sequence compared to the usual sequence that gives the optimal convergence rate. 

@@

            The proof is very intense algebratically hence before we step into it, we present the following intermediate results in advance to their proofs given at the end. 

@@

                \item [(a)] Theorem \ref{thm:pg-ineq}, with $z = z_k$, $k \ge 0$. We can use it because $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth} . 

@@

                \item [(d)] The equality $z_k - y_k = (L_k - \mu)^{-1}((L_k\alpha_k - \mu)(\bar x - v_k) + \mu(1 - \alpha_k)(\bar x - x_{k - 1}))$ for all $k \ge 0$. 
                \item [(e)] The equality $z_k - x_k = \alpha_k(\bar x - v_k)$ for all $k \ge 0$. 
                \item [(f)] The following equality: 

@@

                \item [(g)] The following equality: 

@@

                \item [(h)] The equality: 

@@

                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2

@@

                -\frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2\\ 

@@

                    \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} \Vert \bar x - v_{k - 1}\Vert^2

@@

                \right)\Vert \bar x - v_{k - 1}\Vert^2

@@

                \\ & \quad

@@

            The inequality from previously simplifies and it has: 

@@

            Finally for the base case, when $\alpha_0 = 1$, it has $y_0 = v_{-1} = x_{-1}$, and it makes $z_0 = \bar x$ therefore this makes the proximal gradient inequality into:

@@

                \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{\alpha_{k - 1}^2 L \rho_{k - 1}(1 - \alpha_k)}{2}

@@

    \subsection{stochastic accelerated proximal gradient}
        The following assumption about the objective function is fundamental in incremental gradient method for Machine Learning, data science other similar tasks. 
        \begin{assumption}[sum of many]\label{ass:sum-of-many}
            Define $F := g + (1/n)\sum_{i = 1}^{n} f_i$, assume that $f_i:\RR^n \rightarrow  \RR$ are all $K_i$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K_i > \mu^{(i)}$ and, $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
            Consequently, the function $f$ cane be written as $F = g + f$ where $f = (1/n)\sum_{i = 1}^{n} f_i$ and it satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = \max_{i = 1, \ldots, n}K_i$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$. 
        \end{assumption}
        This assumption is stronger than Assumption \ref{ass:smooth-plus-nonsmooth}. 
        The interpolation hypothesis from Machine Learning stated that the model has the capacity to perfect fit all the observed data. 
        \begin{assumption}[interpolation hypothesis]\label{ass:interp-hypothesis}
            Suppose that $F := f + (1/n)\sum_{i = 1}^{n} f_i$ satsifying Assumption \ref{ass:sum-of-many}. 
            In addition, assuming that it has $0 = \inf_{x}F(x)$ and, there exists some $\bar x \in \RR^n$ such that for all $i = 1, \ldots, n$ it satisfies $0 = f_i(\bar x)$. 
            Obviously, all such $\bar x$ forms the set of minimizers of $F$. 
        \end{assumption}

        \begin{definition}[SNAPG]\label{def:snapg}
            Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
            Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
            Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
            The SAGD generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
            \begin{align*}
                & L_k/L_{k - 1}(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu^{(I_k)}/L_k\right), \\
                & \tau_k = L_k(1 - \alpha_k)\left(L_\alpha \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
                & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
                & x_k =  T_{L_k}(y_k | F_{I_k}) \text{ s.t: } D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
            \end{align*}
        \end{definition}
        \begin{remark}
            The sequence $\alpha_k$ is a random variable because it changes according to variable $I_k$ at the current iteration.
            This decision is made because if Theorem \ref{thm:pg-ineq} needs to hold during each iteration of the algorithm.
        \end{remark}

        \begin{theorem}[SNAPG one step inequality]\label{thm:snapg-one-step}

@@

>>>>

% special operators and stuff introduced for this file.

\newcommand{\cov}{\ensuremath{\operatorname{Cov}}}

\begin{document}
\title{{\fontfamily{ptm}\selectfont Lorum ipsum}}

@@

        \begin{definition}[Bregman Divergence]
            Let $f:\RR^n \rightarrow \overline \RR$ be a differentiable function. 
            Then, for all the Bregman divergence $D_f: \RR^n \times \dom\nabla f \rightarrow \RR$ is defined as: 
            \begin{align*}
                D_f(x, y) := f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
            \end{align*}
        \end{definition}
        \begin{remark}
            If, $f$ is $\mu \ge 0$ strongly convex and $L$ Lipschitz smooth then, its Bregman Divergence has for all $x, y \in \RR^n$: $\mu/2 \Vert x - y\Vert^2 \le D_f(x, y) \le L/2 \Vert x - y\Vert^2$. 
        \end{remark}

@@

        \begin{definition}[similar triangle representation of NAPG]\;\label{def:st-method}\\
            Let $(\alpha_k)_{k \ge 0}$ be an R-WAPG sequence. 
            Suppose that the base case $v_{-1}, x_{k - 1}\in \RR^n$ is given to initialize the algorithm. 
            Then the algorithm produces the sequence of iterates $(y_k, x_k, v_k)_{k \ge 0}$ and auxiliary parameter sequence $L_k, \tau_k$ satisfying these inequalities: 
            \begin{align*}
                & \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}, 
                \\
                & y_k = (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1},
                \\
                & D_f(x_k, y_k) \le L_k/2\Vert x_k - y_k\Vert^2, 
                \\
                & x_k = T_{L_k}(y_k),
                \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
            \end{align*} 
        \end{definition}
        The following theorems are critical in analyzing the behavior of algorithm in Definition \ref{def:st-method}. 
        \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
            Let function $F$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, so it's $\mu \ge 0$ strongly convex. 
            For all $x\in \RR^n$, define $x^+ = T_L(x)$, then there exists a $B \ge 0$ such that $D_f(x^+, x) \le B/2 \Vert x^+ - x\Vert^2$. 
            Then, for all $z \in \RR^n$ it satisfies proximal gradient inequality at point $x$:  
            \begin{align*}
                0&\le F(z) - F(x^+) - \frac{B}{2}\Vert z - x^+\Vert^2  + \frac{B - \mu}{2}\Vert z - x\Vert^2
                \\
                &=  F(z) - F(x^+) - \langle B(x - x^+), z - x\rangle
                - \frac{\mu}{2}\Vert z - x\Vert^2
                - \frac{B}{2}\Vert x - x^+\Vert^2. 
            \end{align*}
            Since $f$ is assumed to be $L$ Lipschitz smooth, the above condition is true for all $x, y \in \RR^n$ for all $B \ge L$. 
        \end{theorem}
        \begin{remark}
            The theorem is the same as in Nesterov's book \cite[Theorem 2.2.13]{nesterov_lectures_2018}, but with the use of proximal gradient mapping and proximal gradient instead of project gradient hence making it equivalent to the theorem in Beck's book \cite[Theorem 10.16]{beck_first-order_2017}. 
            The only generalization here is parameter $B$ which made to accommodate algorithm that implements Definition \ref{def:st-method} with some line search routine. 
        \end{remark}
        \begin{theorem}[Jensen's inequality]\label{thm:jesen}
            Let $F: \RR^n \rightarrow \overline \RR$ be a $\mu \ge 0$ strongly convex function. 
            Then, it is equivalent to the following condition. 
            For all $x, y \in \RR^n$, $\lambda \in (0, 1)$ it satisfies the inequality 
            \begin{align*}
                (\forall \lambda \in [0, 1])\; 
                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert y - x\Vert^2. 
            \end{align*}
        \end{theorem}
        \begin{remark}
            If $x, y$ is out of $\dom F$, the inequality still work by convexity. 
        \end{remark}

@@

        The following theorem provides a complete proof for the convergence rate of algorithms implementing Definition \ref{def:st-method}, which is equivalent to NAG, or NAPG. 
        It made use of Definition \ref{def:rwapg-seq} which accommodates a relaxed sequence compared to the usual sequence that gives the optimal convergence rate. 

@@

            The proof is very intense algebraically hence before we step into it, we present the following intermediate results in advance to their proofs given at the end. 

@@

                \item [(a)] Theorem \ref{thm:pg-ineq}, with $z = z_k$, $k \ge 0$. We can use it because $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 

@@

                \item [(d)] The equality $z_k - y_k = (L_k - \mu)^{-1}((L_k\alpha_k - \mu)(\bar x - v_k) + \mu(1 - \alpha_k)(\bar x - x_{k - 1}))$ for all $k \ge 0$, it comes from Definition \ref{def:st-method}. 
                \item [(e)] The equality $z_k - x_k = \alpha_k(\bar x - v_k)$ for all $k \ge 0$ it comes from Definition \ref{def:st-method}. 
                \item [(f)] Using basic algebra, we have the following equality: 

@@

                \item [(g)] Using (c), we have the following equality: 

@@

                \item [(h)] Definition \ref{def:rwapg-seq} determine the inequality: 

@@

                + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2

@@

                -\frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\ 

@@

                - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\&\quad 
                    + \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} \Vert \bar x - v_{k - 1}\Vert^2

@@

                \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 

@@

                &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2 \\ & \quad

@@

            The inequality from previously simplifies, and it has: 

@@

            Finally, for the base case, when $\alpha_0 = 1$, it has $y_0 = v_{-1} = x_{-1}$, and it makes $z_0 = \bar x$ therefore this makes the proximal gradient inequality into:

@@

                \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{\alpha_{k - 1}^2 L_k \rho_{k - 1}(1 - \alpha_k)}{2}

@@

    \subsection{stochastic accelerated proximal gradient}
        The following assumption about the objective function is fundamental in incremental gradient method for Machine Learning, data science other similar tasks. 
        \begin{assumption}[sum of many]\label{ass:sum-of-many}
            Define $F := g + (1/n)\sum_{i = 1}^{n} f_i$, assume that $f_i:\RR^n \rightarrow  \RR$ are all $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
            Consequently, the function $f$ cane be written as $F = g + f$ where $f = (1/n)\sum_{i = 1}^{n} f_i$ and, it satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = \max_{i = 1, \ldots, n}K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$. 
        \end{assumption}
        This assumption is stronger than Assumption \ref{ass:smooth-plus-nonsmooth}. 
        The interpolation hypothesis from Machine Learning stated that the model has the capacity to perfect fit all the observed data. 
        \begin{assumption}[interpolation hypothesis]\label{ass:interp-hypothesis}
            Suppose that $F := f + (1/n)\sum_{i = 1}^{n} f_i$ satisfying Assumption \ref{ass:sum-of-many}. 
            In addition, assuming that it has $0 = \inf_{x}F(x)$ and, there exists some $\bar x \in \RR^n$ such that for all $i = 1, \ldots, n$ it satisfies $0 = f_i(\bar x)$. 
            Obviously, all such $\bar x$ forms the set of minimizers of $F$. 
        \end{assumption}

        \begin{definition}[SNAPG-V1 \textcolor{red}{DOESN'T WORK WELL}]\;\label{def:snapg-v1}\\
            Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
            Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
            Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
            The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
            \begin{align*}
                & (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu^{(I_k)}/L_k\right), \\
                & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
                & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
                & x_k =  T_{L_k}(y_k | F_{I_k}) \text{ s.t: } D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
            \end{align*}
        \end{definition}
        \begin{remark}
            The sequence $\alpha_k$ is a random variable because it changes according to variable $I_k$ at the current iteration.
            This decision is made because if Theorem \ref{thm:pg-ineq} needs to hold during each iteration of the algorithm.
        \end{remark}

        \begin{theorem}[SNAPG one step inequality \textcolor{red}{INVALIDATED}]
            Let sequences of iterates $(y_k, x_k, v_k)_{k \ge 0}$ satisfy SNAPG (Definition \ref{def:snapg-v1}). 
            Denote $\mathbb E_k [\cdot]$ to be the conditional expectation on $I_{0}, I_1, \ldots, I_{k - 1}$. 
            Then, for all $k \ge 1$ the following inequality is true: 
            $$
            \begin{aligned}
            & - F(\bar x) + 
            \mathbb E_k \left[
                F_{I_k}(x_k)
            \right]
            + \mathbb E_k
            \left[
                \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
            \right]
            &\le (1 - \mathbb E_k [\alpha_k])
                \mathbb E \left[F(x_{k - 1})\right]
                - 
                F(\bar x)
                \mathbb E_k 
                \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2\right]
            \end{aligned}
            $$

@@

            For one step, a specific function $F_{I_k}$ is sampled. 
            $F_{I_k}$ is $K^{(I_k)} > \mu^{(I_k)} \ge 0$ strongly convex and smooth. 
            The iterates $x_k, v_k$ is a function of random variable $I_k$, conditioned on all $I_{k - 1}, I_{k - 2}, \ldots , I_0$
            The sequence $\alpha_k$ is a sequence of random variable and, the relations between $\alpha_k, \alpha_{k - 1}$ is given by: 
                \alpha_k &= 
                    -\frac{L_{k - 1}\alpha_{k - 1}^2}{L_k} + \frac{\mu^{(I_k)}}{L_k} 
                    + \sqrt{
                            \frac{\mu^{(I_k)}}{L_k}
                            - \frac{\alpha_{k - 1}^2L_{k - 1}}{L_k}
                        \right)^2
                        + \frac{\alpha_{k - 1}4L_{k - 1}}{L_k}
            The relationship $(L_{k - 1}/L_k)(1 - \alpha_k)\alpha_{k - 1}^2 = \alpha_k(\alpha_k - \mu^{(I_k)}/L_k)$ is an instance of Definition \ref{def:rwapg-seq} where $\rho_{k - 1} = L_{k - 1}/L_k$. 
            Therefore, the one-step convergence result of \ref{thm:onestep-napg-cnvg} applies to function $F_{I_k}$ with sequence $\alpha_k$ and, it yields: 
                & - F_{I_k}(\bar x) + F_{I_k}(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                & \le 
                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
            We take the conditional expectation on the LHS and, it has 
                & \mathbb E_k 
                \left[
                    - F_{I_k}(\bar x) + F_{I_k}(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \right]
                \mathbb E_k \left[- F_{I_k}(\bar x)\right]
                \mathbb E_k \left[F_{I_k}(x_k)\right]
                \mathbb E_k \left[
                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \right]
                &\underset{\text{(a)}}{=} 
                - F(\bar x) + 
                \mathbb E_k \left[
                    F_{I_k}(x_k)
                \right]
                + \mathbb E_k
                \left[
                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \right]. 
            At label (a), we make use of interpolation hypothesis which makes $\mathbb E_k[F_{I_k}(\bar x)] = F(\bar x)$. 
            Next, taking the conditional expectation on the RHS it has 
                & \mathbb E_k\left[
                    (1 - \alpha_k)
                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
                \right]
                &\underset{\text{(b)}}{=}
                \mathbb E_k\left[1 - \alpha_k\right]
                \mathbb E_k
                    \left[
                        F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
                    \right]
                &\neq 
                \mathbb E_k
                \left[1 - \alpha_k\right]
                \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] - F(\bar x)
                    \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2\right]
            At (b), we need to make use of covariance between the two random variable... 
            Consider random variables $X_k = (1 - \alpha_k)$ and $Y_k = F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \alpha_{k - 1}L_{k - 1}/2\Vert \bar x - v_{k - 1}\Vert^2$ which are functions of $I_k$ conditioned on $\alpha_{k - 1}$ and, $x_{k - 1}, v_{k - 1}$. 
            The conditional expectation of their product has $\mathbb E_k[X_kY_k] = \mathbb E_k[X_k] \mathbb E_k[Y_k] + \cov[X_k, Y_k]$.
            \textcolor{red}{Hence, taking the expectation doesn't follow. }

        \begin{definition}[SNAPG-V2]\label{def:snapg-v2}
            Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
            Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
            Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
            The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
            \begin{align*}
                & (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right), \\
                & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
                & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
                & x_k =  T_{L_k}(y_k | F_{I_k}) \text{ s.t: } D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
            \end{align*}
        \end{definition}

        \begin{theorem}[SNAPG-V2 one step convergence]

        \end{theorem}
        \begin{proof}
            Let's suppose that $I_k = i$ and, for all $k \ge 0$ let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
            From Definiton \ref{def:snapg-v2}, it has
            \begin{align*}
                (1 + \tau_k)^{-1}
                &\underset{\eqref{thm:onestep-napg-cnvg-i}}{=} 
                \left(
                    1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
                \right)^{-1} = \left(
                    \frac{L_k\alpha_k - \mu^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
                \right)^{-1}
                = \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}. 
            \end{align*}
            Therefore, for all $k \ge 0$ $y_k$ has 
            \begin{align*}
                y_k &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1}
                \\
                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} 
                \left(
                    v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}} x_{k - 1}
                \right)
                \\
                &= 
            \end{align*}
        \end{proof}
